SAT Competition 2020\tnoteref{title}

### 2020-12-27 paper/main.tex
JKU address
parallel solvers

\subsection{Planning Sub-Track}
% - 86 out of 100 biggest (number of clauses) are planning
% - 109 / 200 in the planning track are not solved by any solver
    % - 186 / 600 in total
% - all 200 above 90\% binary clauses and half have above 99%
The instances of the planning sub-track are big compared to the rest of the
main track. Using the number of clauses as a metric; out of the $100$ biggest
instances
% of the main-track
$86$ belong to the planning track. The large size can mainly be attributed to
binary clauses. On average, more than $98$\% of the clauses are binary for
planning instances, where the average for the rest of the instances from the
main track is below $60$\%.

Despite the large size, only a few instances directly caused memory problems for
more than just a few solvers. In most cases the \SI{128}{\giga\byte} of RAM
available were sufficient.
% The saving grace might have been
% This can be attributed to
% the \SI{128}{\giga\byte} of RAM available to each solver.
However, the three biggest instances from the \emph{childsnack} family of
planning problems encoded with the \emph{hierarchical} planner \emph{Tree-REX}
caused over half of the solvers to abort with some error message related to
memory. Other solvers were still able to solve the same instances within $300$
seconds.

\subsection{Similarity of Solvers}
To investigate how similar the solvers of the main track are to each other, we
define a similarity metric based on the measured runtimes. For that we first
remove $186$ benchmarks from the collected data that have not been solved by any
solver. For the rest of the benchmarks we use the PAR-2 score,
% based on the \num{5000}-second timeout
i.\,e., for each solver we set a score of \num{10000} for unsolved instances.
This leaves us with $414$ floats
$S_{1},\dots,S_{n}$ for each solver $S$. The similarity for two solvers $A$
and $B$, normalized to the interval $[0,1]$ is defined
% as:
by Equation~\ref{eq-similarity}.

\begin{equation}
\label{eq-similarity}
	similarity(A, B) =\quad 1 - \frac{\sum{|A_{i} - B_{i}|}}{414 \cdot 10000}
\end{equation}
We calculated the \emph{similarity} between the $30$ solvers which achieved the
best PAR-2 score in the main track. The results are displayed in
Figure~\ref{fig-similarity-main} as a \emph{heat map}. Additionally the result
of hierarchically clustering the solvers based on their similarity is
illustrated as a \emph{dendrogram}. The height at which two solvers or clusters
are joined reflects how similar they are. For example
enabling the \emph{trail saving} in \emph{CaDiCaL-alluip} has no impact on the
runtime, resulting in a similarity above \num{0.999}. Thus the two solvers are joined very low in the dendrogram.
% A similar visualization was used in the SAT Challenge 2012 \todo{cite}. They used

One big cluster we can identify are the \emph{Mapel} decedents in the lower left
corner, all of which are modifications of the winners of the SAT Competition
2018 and the SAT Race 2019. \todo{I think... also race vs competition? Sorry I am new
  here NF} The solver \emph{mergesat} does not quite fit into the cluster and
has a comparatively high similarity to the \emph{CryptoMiniSat} (\emph{CMS})
family at the top right. With the exception of \emph{mergesat} and maybe
\emph{DurianSat} we observe a high similarity within the cluster.

The three \emph{Relaxed} solvers by \emph{Zhang} and \emph{Cai} are using the
same code base as a lot of the solvers in the Maple-Cluster but their overall
performance is better and closer to the CMS-Cluster.

The CMS versions differ in their implementation of stochastic local search (SLS)
but overall have a similar performance.

The last big cluster in the center of the heat map is comprised of the solvers
originally written by Biere. The three configurations of \emph{Kissat} form a
subcluster, even though the configurations are fairly distinct from each other.
% , specialized for satisfiable and unsatisfiable instances.
% One targets satisfiable instances, while the other is focused on unsatisfiable
% instances and a third alternating between them.

The other subcluster consists of
modifications to the 2019 version of \emph{\mbox{CaDiCaL}}. The new version
CaDiCaL-2020 has a worse overall performance than
% has an overall worse per
% is lacking behind
the other solvers in this cluster.

\begin{figure}[tp]
    \centering
    \includegraphics[width=\linewidth]{similarity/cross.pdf}
    \caption{Heat-map and dendrogram (top) based on the runtime similarity of the solvers participating in the main track.
      % Similarity is defined as
      % one minus the average taxicab distance normalized to the interval [0,1].
      % Spearman's rank correlation coefficient.
      Darker regions mean that the solvers are more similar.
      A more precise relation between color and similarity-value together with a histogram of the values that appear is given at the bottom.
    }
    \label{fig-similarity-main}
\end{figure}

% To estimate the similarity between the performance of the solvers of the Main
% Track we define a similarity metric $s$.
% identify each solver with a point in the 600-dimensional real vector
% space. Each component describes the PAR-2 runtime on one instance. We map the
% taxicab distance to the $[0, 1]$ interval and then to determine how similar two
% solvers are.

@@

\begin{table}[b]
\smaller
\centering
\begin{tabular}{|l|l|l|}
\hline
\bf Team & \bf Solver & \bf Awards\\
\hline
\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
 & P-MCOMSPS-STR-32 & \firsto \firsts \secondu \\
 & P-MCOMSPS-STR-64 & \firsto \\
\hline
\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}
 & Plingeling & \secondo \thirds \firstu \\
 & Treengeling & \\
\hline
\multirow{2}{*}{Nabeshima, Inoue}
 & ManyGlucose-32 & \thirdo \thirdu \\
 & ManyGlucose-64 & \thirdu \\
\hline
\multirow{2}{*}{Tchinda, Djamegni}
 & painlessmaplevone & \seconds \\
 & painlessmaplevtwo & \seconds \\
\hline
Li, Wu, Xu, Chen & syrupscavel & \\
\hline
Chen & abcdsatptwenty & \\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the parallel track.}
\end{table}

\subsubsection{P-MCOMSPS-STR}

P-MCOMSPS-STR is built from the Painless framework~\cite{Frioux:2017:Painless} for solver parallization and uses the MapleCOMSPS solver~\cite{Liang:2017:Maplecomsps} as a building block. 
The authors submitted a 32 and 64 core version and won 3 awards, first place in the overall ranking, first place in the SAT ranking and second in the UNSAT ranking. 
The 64 core version performed slightly worse than the 32 core version in the overall ranking, and that gap is bigger for the SAT-only ranking and worst for the UNSAT-only ranking, such that in the separate rankings only the 32 core version is responsible for winning the prices.

The painless framework uses a generic interface to integrate a solver and abstracts away the implementation details of parallelism and concurrenct data-structures, such that implementations within the framework boil down to implementing parallelization and clause sharing strategies.

In the submitted version of P-MCOMSPS-STR, diversification is done via diverse fixed configurations of branching strategies (LRB and VSIDS) and sparse random intialization of variable polarities like in~\cite{Balyo:2015:Hordesat}. 
One instance of their ``sequential engines'' performs concurrent clause strengtheing as described in~\cite{Wieringa:2013:CCS} and another single instance is configured to perform Gaussian eliminiation during preprocessing.

For sharing they use an all-to-all strategy with a regular exchange of a fixed size buffer and a dynamic clause lbd limit.

@@

Plingeling got three awards, first place in the Unsat Category, third place in Sat and second place in the overall evaluation. 
Plingeling is an extension of the well-known SAT solver Lingeling~\cite{} and did not change since 2016. 
Via a global master queue, Plingeling shares unit clauses, equivalences and short clauses with clauses with at most 40 literals and glucose LBD level of at most 8 and random seeds, e.g., for diversification via default polarities.~\cite{}

@@

The authors of ManyGlucose received two awards in this competition. 
ManyGlucose was submitted in 32-core and 64-core variants~\cite{}.
The 32-core variant won two third prices, one in the overall evaluation and one in the unsat sub-track. 
ManyGlucose is a fork of GlucoseSyrup~\cite{} and uses strategies similar to those known from ManySAT~\cite{} in order to achive deterministic solver runs.

@@

The authors Painless Maple received one award for second best performance in the Sat sub-track of the parallel track. 
However, the solver was last in the Unsat sub-track.

The authors implemented a couple of modifications (\todo{name them}) on top of the MapleLCMDistChronoBT~\cite{} solver, which they also submitted in various configurations to the main track. 
The two submissions in the parallel track use painless as a parallelization framework.

Their sharing strategy includes splitting their workers into two categories, where the solvers in the first category only export clauses and only solvers in the second category import and export clauses.

They submitted two variants with different diversification strategies. 
In their first variant they use different configurations of configurations of the newly implemented strategies. 
The second variant uses a more classic diverisification strategy by randomizing polarities and variable scores.

@@

\begin{table}[ht]
\smaller
\centering
\begin{tabular}{|l|l|l|}
\hline
\bf Team & \bf Solver & \bf Rank\\
\hline
Schreiber & mallob-mono & 1\\
\hline
\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & TopoSAT2 & 2\\
\hline
Riveros & Slime & 3\\
\hline
\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & Paracooba & -\\
& Paracooba-March & -\\
\hline
Hartung & CTSat & -\\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the cloud track.}
\end{table}

>>>>

\todo{Similarity of Solvers: Rank Correlation}

@@

\begin{table}[b]
\smaller
\centering
\begin{tabular}{|l|l|l|}
\hline
\bf Team & \bf Solver & \bf Awards\\
\hline
\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
 & \solver{Painless-MCOMSPS-STR-32} & \firsto \firsts \secondu \\
 & \solver{Painless-MCOMSPS-STR-64} & \firsto \\
\hline
\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}
 & \solver{Plingeling} & \secondo \thirds \firstu \\
 & \solver{Treengeling} & \\
\hline
\multirow{2}{*}{Nabeshima, Inoue}
 & \solver{ManyGlucose-32} & \thirdo \thirdu \\
 & \solver{ManyGlucose-64} & \thirdu \\
\hline
\multirow{2}{*}{Tchinda, Djamegni}
 & \solver{painlessmaplevone} & \seconds \\
 & \solver{painlessmaplevtwo} & \seconds \\
\hline
Li, Wu, Xu, Chen & \solver{syrupscavel} & \\
\hline
Chen & \solver{abcdsatptwenty} & \\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the parallel track.}
\end{table}

\subsubsection{Painless Maple-CoMinisatPS STR}

\solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless}~\cite{Liang:2017:Maplecomsps}. 
The authors submitted a \solver{32 core} and a \solver{64 core} variant and were awared three prices: first place in the Main track, first place in the Sat track and second in the Unsat track. 
The \solver{32 core} variant achieved slightly better scores than the \solver{64 core} variant. 
The differentiated evaluation of the Sat and Unsat tracks shows the \solver{32 core} variant performed much better, such that the follow-up solvers outperformed the \solver{64 core} variant.

\solver{Painless} uses a generic interface to integrate a solver and abstracts away the implementation details of parallelism and concurrenct data-structures, such that implementations in \solver{Painless} boil down to implementing parallelization and clause sharing strategies.

\solver{Painless-MCOMSPS-STR} diversifies mainly via diverse fixed configurations of the branching strategies LRB and VSIDS, and sparse random intialization of variable polarities~\cite{Balyo:2015:Hordesat}. 
However, a special solver instance performs concurrent clause strengthening~\cite{Wieringa:2013:CCS}. 
Another special solver instance is configured to perform Gaussian eliminiation during preprocessing. 
\solver{Painless-MCOMSPS-STR} uses an all-to-all strategy for clause sharing with a fixed size clause buffer and an LBD filter with a dynamic limit.

@@

\solver{Plingeling} got three awards: first place in the Unsat track, second place in the Main track, third place in the Sat track. 
\solver{Plingeling} is built around the well-known \solver{Lingeling} and did not change since 2016. 
In a global master queue, \solver{Plingeling} shares unit clauses, equivalences and short clauses with a size limit of~$40$ and an LBD limit of~$8$. 
\solver{Plingeling} uses random seeds for diversification via default polarities~\cite{Biere:SC2020,Biere:2012:Lingeling}.

@@

\solver{ManyGlucose} was submitted in \solver{32 core} and \solver{64 core} variants. 
The \solver{32 core} variant received two awards in this competition: one third place in the Main track and another third place in the Unsat track. 
\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achive deterministic solver behaviour~\cite{GlucoseSyrup}~\cite{ManySat}.

@@

\solver{Painless Maple} received the award for second best performance in the Sat track but scored last in the Unsat track. 
\solver{Painless Maple} integrates the solver \solver{ExMapleLCMDistChronoBT}, which is a modified \solver{MapleLCMDistChronoBT} (see Main track), in the \solver{Painless} parallelization framework.

\solver{Painless Maple} uses a sharing strategy in which the solvers are divided into those which only export clauses and others which import \emph{and} export clauses. 
\solver{Painless Maple} was submitted in two variants \solver{v1} and \solver{v2}. 
\solver{Painless Maple v1} diversifies via hand-crafted heuristic configurations and \solver{Painless Maple v2} diversifies via randomized intialization of branching heuristics.

@@

\begin{table}[t]
\smaller
\centering
\begin{tabular}{|l|l|l|}
\hline
\bf Team & \bf Solver & \bf Rank\\
\hline
Schreiber & mallob-mono & 1\\
\hline
\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & TopoSAT2 & 2\\
\hline
Riveros & Slime & 3\\
\hline
\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & Paracooba & -\\
& Paracooba-March & -\\
\hline
Hartung & CTSat & -\\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the cloud track.}
\end{table}
